### 2015-03-02 fundamentals/impl.tex
removes redundant sentence about nose, for brevity
removes aside about the implementation of regression tests, for brevity

Regression tests ensure significant unintended changes do not
occur over the course of \Cyclus development. Such a change is called a
\emph{regression} because the new version is almost always wrong.
Regression tests are implemented similarly to integration tests.
Nose is used to execute full \Cyclus simulations whose results
are then compared. In this category, however, the comparison is done against
the output of the same input file when run with a previous version of \Cyclus,
typically the last released version.
In some sense, regression tests are `dumb' in that they do
not care about the contents of a simulation being correct, only whether or not
it changed. They pick up glaring time-sensitive mistakes that may
not appear elsewhere, though they do not purport to make claims about the
quality of the physics modeled. Regression tests are primarily implemented
in \Cycamore because its archetypes are sophisticated enough
to make interesting simulations.

>>>>

Regression tests ensure significant unintended changes do not
occur over the course of \Cyclus development. Such a change is called a
\emph{regression} because the new version is almost always wrong.
Regression tests are implemented similarly to integration tests.
In this category, however, the comparison is done against
the output of the same input file when run with a previous version of \Cyclus,
typically the last released version.
In some sense, regression tests are `dumb' in that they do
not care about the contents of a simulation being correct, only whether or not
it changed.
